Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-10-14 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient }}

@@

            In this inequality, observe that the parameter $\epsilon$ controls the inexactiness of the proximal gradient evaluation. 
            Morespecifically, $\epsilon_k$ controls the absolute pertubatnions of the proximal gradient inequality compared to its exact counterpart. 
            $\rho$ on the otherhand, it is the over-relaxation of proximal gradient operator and it compensates the pertubations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$. 

@@

        Recall that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, if we choose $x = y_k$ so $\tilde x = x_k \approx_\epsilon T_{L_k}(y_k)$, and set $z = z_k, \epsilon = \epsilon_k$ then Theorem \ref{thm:inxt-pg-ineq} has: 

@@

    \subsection{convergence results of the outer loop}

@@

        \begin{lemma}[the properties of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}, then $\forall k\ge 1\; \alpha_k \in (0, 1)$ and, in addition the sequence $(\beta_k)_{k \ge 0}$ has

@@

            We prove using induction, inductively assume that $\alpha_k \in (0, 1]$. 
            We can solve for $\alpha_k$ using the recursive equality which should always have one of the strictly positive root given by: 

@@

            At (1) we completed a square inside of the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 

@@

                \item $\alpha_0 = 1, p > 0$;

@@

@@

            Pay close attention that $\alpha_k$ had been determined in the above theorem, and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence is bounded above. 

@@

@@

    \subsection{the fastest rate of which the error schedule can shrink}

@@

        \begin{lemma}[error schedule lower bound]

@@

@@

        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma)$

@@

            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2, g(v) = \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$. 

@@

            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 

@@

    \subsection{error bound and linear convergence}
        The following theorem characterize linear convergence of the proximal gradient method under gradient mapping error bound condition. 

@@

            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ the inequality: 

@@

    \subsection{characterizing linear convergence of the proximal problem}
        In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]
            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
        \end{proposition}
        \begin{proof}
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator function which represents a box constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also. 
            \par
            Let $\mu_f = \lambda\Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
            \begin{align*}
                \gamma = \frac{\kappa_f}{1 + \mu_f + \sqrt{1 + \mu_f}}. 
            \end{align*}

        \end{proof}
        \par
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[inner loop linear convergence scenario 1]\label{prop:inn-loop-lin-cnvg}

        \end{proposition}
    \subsection{inner loop complexity}

>>>>

\title{{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient With Error Bound Conditions gives Near Optimal Convergence Rate }}

@@

            In this inequality, observe that the parameter $\epsilon$ controls the inexactness of the proximal gradient evaluation. 
            More specifically, $\epsilon_k$ controls the absolute perturbations of the proximal gradient inequality compared to its exact counterpart. 
            $\rho$ on the other hand, it is the over-relaxation of proximal gradient operator, and it compensates the perturbations caused by $\epsilon$ relative to the term $\Vert \tilde x - x\Vert^2$. 

@@

        Recall that $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}, if we choose $x = y_k$ so $\tilde x = x_k \approx_{\epsilon_k} T_{L_k}(y_k)$, and set $z = z_k, \epsilon = \epsilon_k$ then Theorem \ref{thm:inxt-pg-ineq} has: 

@@

    \subsection{Convergence results of the outer loop}

@@

        \begin{lemma}[the optimal momentum sequence is indeed valid and optimal]\;\label{lemma:opt-mmntm-seq}\\
            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}. 
            If we choose $\alpha_0 \in (0, 1]\;$ then it satisfies $\alpha_k \in (0, 1)\;\forall k\ge 1$, and it's given by: 
            In addition, the sequence $(\beta_k)_{k \ge 0}$ has

@@

            We will prove using induction.
            Assume inductively that $\alpha_k \in (0, 1]$. 
            We can solve for $\alpha_k$ using the recursive equality from Assumption \ref{ass:opt-mmntm-seq} which always has one of the strictly positive root given by: 

@@

            At (1) we completed a square inside the radical, and use the assumption that $\alpha_k > 0$ and, $L_k > 0, L_{k - 1} > 0$ because we had $B_k > 0$: 

@@

                \item it has $p > 0$;

@@

                \hspace{-0.7em}\le 

@@

            Pay attention that $\alpha_k$ had been determined in the above theorem (as seemed in Lemma \ref{lemma:opt-mmntm-seq}), and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence to be bounded above. 

@@

            Finally, observe that from the above proof, in case when $p = 1$, the convergence rate would be $\mathcal O(\log(k)/k^2)$. 

@@

    \subsection{The fastest rate of which the error schedule can shrink}

@@

        \begin{lemma}[error schedule lower bound]\;\label{lemma:err-schedule-lbnd}\\
            Let, $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(\beta_k)_{k\ge 0}, \mathcal E_0, p$ be given by Assumption \ref{ass:opt-mmntm-seq}, $L_k := \rho_k + B_k$. 
            Let $(\epsilon_k)_{k \ge 0}$ be given by $\epsilon_k := \frac{\mathcal E_0 \beta_k}{k^p} + \rho_k \frac{\Vert x_k - y_k\Vert^2}{2}$, then it will be a valid error sequence and so that it satisfies the assumption. 
            If in addition, there exists $L_{\min}$ such that for all $k\ge 0$ such that it has $L_{\min} \le \min_{1 \le i \le k}L_i$ and, we assume $\mathcal E > 0$, then $\epsilon_k$ admits the non-trivial lower bound: 
                \epsilon_k \ge \frac{\mathcal E_0}{k^p}\left(
                    1 + k \alpha_0 \sqrt{L_0} \sqrt{L_{\min}^{-1}}
                \right)^{-2} \ge \mathcal O(k^{-2-p}). 

@@

            Recall Assumption \ref{ass:valid-err-schedule}, the largest valid error schedule is $\epsilon_k = \frac{\mathcal E_0 \beta_k}{k^p} + \rho_k \frac{\Vert x_k - y_k\Vert^2}{2}$. 
            Then it has 
                \epsilon_k &\ge \frac{\mathcal E_0 \beta_k}{k^p}
                &\underset{(1)}{\ge} 
                \frac{\mathcal E_0\beta_k}{k^p}
                &\underset{(2)}{\ge}
                \frac{\mathcal E_0\beta_k}{k^p}
                    1 + k\alpha_0\sqrt{L_0}\sqrt{L_{\min}^{-1}}
                &\ge \mathcal O(k^{-2-p}). 
            At (1), we used Lemma \ref{lemma:opt-mmntm-seq}. 
            At (2), we used that $L_{\min} \le L_i$ for all $i = 0, 1, 2, \ldots$. 

@@

        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma_\lambda)$

@@

            \item Let function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$. 

@@

            \item Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 

@@

    \subsection{Error bound and linear convergence}
        The following theorem characterizes linear convergence of the proximal gradient method under gradient mapping error bound condition. 

@@

            Under this assumption, the iterates $(x_k)_{k \ge 0}$ given by Definition \ref{def:ista} satisfies for all $k \ge 0, \bar x \in S$ and $\tau \ge L$ the inequality: 

@@

    \subsection{Conditions for linear convergence of the proximal problem}
        In this section, we will focus on the sufficient characterization of the proximal problem which allows proximal gradient method to achieve linear convergence rate. 
        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
        \begin{proposition}[1-norm problem]\label{prop:1nrm-prox-problem}
            Let $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
        \end{proposition}
        \begin{proof}
            Take note that the dual has closed form $g^\star(z) =\delta(z | \{x : \Vert x\Vert_1 \le 1\})$. 
            The $g^\star$ is an indicator function which represents a box constraint. 
            The objective function $\Psi_\lambda(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2$ so it's Lipschitz smooth, and it must have a set of minimizers $S$ because its domain is compact. 
            In addition, $\Psi_\lambda$ fits the assumption of Necoara et al. \cite[Theorem 8]{necoara_linear_2019}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also. 
            \par
            Let $\mu_f = \Vert A\Vert^2/\kappa_f$, let $\kappa_f = \theta^{-2}(A, C)$ be the Hoffman Constant as presented by Necoara et al. in \cite[Section 4]{necoara_linear_2019} where $C$ is the constraint matrix of the inequality set $\delta(z | \{x : \Vert x\Vert_1 \le 1\})$, then the error bound constant can be satisfied with
            \begin{align*}
                \gamma_\lambda = \frac{\kappa_f}{1 + \lambda\mu_f + \sqrt{1 + \lambda\mu_f}}. 
            \end{align*}
        \end{proof}
        \begin{remark}
            The error bound constant $\gamma$ is very difficult to obtain an lower estimate in practice. 
        \end{remark}
        \par
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[inner loop linear convergence scenario I]\label{prop:inn-loop-lin-cnvg}

        \end{proposition}
        The following proposition characterizes another case where error bound conditions of problem problem holds. 
        \begin{proposition}[nonsmooth PLQ linear composite]\label{prop:plq-prox-problem}

        \end{proposition}
    \subsection{Inner loop complexity}
        In this section, we will estimate the total number of iterations in the inner loop to achieve a certain accuracies $\epsilon$ on primal objective $\Phi_\lambda$ of the proximal problem for some given $\lambda > 0$. 
        We will specify the context for parameters $\epsilon, \lambda$ in relation to the outer problem of obtaining $x_k \approx_{\epsilon_k} T_{B_k + \rho_k}(y_k)$.

### 2025-10-14 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, changes

% THEMES AND BEAMER SETTINGS ===================================================
% \usetheme{Madrid}
\graphicspath{{.}}
\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
\setbeamertemplate{blocks}[rounded][shadow=true]
\setbeamertemplate{navigation symbols}{} 
% \setbeamercolor{block title}{bg=cyan,fg=black}  % CHANGE THE BLOCK STYLE IN BEAMER. 
% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.

@@

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date[\today]{\today \\ \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}}
\subject{Nesterov's acceleration and its applications}

@@

\section{Introduction and background}
    \subsection{Motivations}
        \begin{frame}{Nesterov's accelerated gradient in 1983}
            Let's recall a classic. 
            \begin{block}{Nesterov's accelerated gradient in 1983}
                Initialized $x_0 = y_0 \in \RR^n$. 
                The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
                    & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
                    & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
                    & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
            \end{block}
            If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 
            \begin{itemize}
                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;
                \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
            \end{itemize}
        \begin{frame}{Other choices for the momentum sequence}
            Generalized by Beck \cite{beck_fast_2009-1} in 2009, called FISTA, it has $(t_k)_{k}$: 
                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
            Chambolle and Dossal in 2015 \cite{chambolle_convergence_2015}, if $t_k = (k + a -1)/a$, then$(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.
            In Nesterov's book \cite{nesterov_lectures_2018} and Beck's book \cite{beck_first-order_2017} that if in addition, $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, with Strongly convex with $\mu > 0$, then $(\theta_k)_{k\ge 0}$: 
                   \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}. 
            It gives $\mathcal O((1 - \sqrt{\mu/L})^k)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 

@@

        \begin{frame}{A major question}
            This is a question that lead our investigation: 

@@

@@

                    \item A minimizer exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.

@@

            \textbf{This assumption the full scope of the theoretical and practical discussion, assume it throughout.}

@@

            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ that has an upper bound of: 

@@

@@

@@

        \begin{frame}{A practical realization inspired by the theories}
            Our theories suggest that, the upperbound for function value in the R-WAPG algorithm is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
            \textbf{Taking this idea further, this is what we did for numerical experiments}: 

@@

                We made a Free R-WAPG algorithm which estimates the strong convexity constant $\mu$ through the Bregman Divergence at two successive iterates while the algorithm is running and, we check the upper bound using our convergence theory. 

@@

@@

            In this section, we highlight key theoretical results that allowed us to unify convergence rate for various variants of FISTA in the literature.
            \begin{definition}{R-WAPG sequences}\label{def:rwapg-seq}

@@

                Let $(\alpha_k)_{k \ge 0}$ be such that: 
                    & \alpha_0 \in (0, 1], \\
                    & \alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1). 
                Define $(\rho_k)_{k \ge 0}$
                    \rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{
                        (1 - \alpha_{k + 1}) \alpha_k^2.
                We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 

@@

                The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:

@@

                        g_k &= \mathcal G_L (y_k),

@@

                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k),

@@

            After six pages of math in the paper, we deduced the following theorem: 

@@

                    & \begin{aligned}

@@

                        &= x_{k} +
                        \frac{\rho_{k - 1}\alpha_{k - 1}(1 - \alpha_{k - 1})}
                        {\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_{k}}(x_{k} - x_{k - 1}), 
                    \end{aligned}

@@

                    & x_{k + 1} =
                    y_k - L^{-1} \mathcal G_L (y_k),

@@

                        x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k).
                    \end{aligned}

@@

            If $\mu = 0$, then it simplifies:

@@

                If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:

@@

                    \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.

@@

        \begin{frame}{In addition, our theory made a new prediction}

@@

                \item It allows $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 

@@

            This insipired our numerical experiments. 

@@

\section{References and draft on arxiv}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}

>>>>

% THEMES AND BEAMER SETTINGS ===================================================
% \usetheme{Madrid}
\graphicspath{{.}}
\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
\setbeamertemplate{blocks}[rounded][shadow=false]
\setbeamertemplate{navigation symbols}{} 
% \setbeamercolor{block title}{bg=cyan,fg=black}  % CHANGE THE BLOCK STYLE IN BEAMER. 
% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.

@@

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date[\today]{
    \today 
    \\
    2025 Annual Midwest Optimization Meeting
    \\ 
    \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}
}
\subject{Nesterov's acceleration and its applications}

@@

\section{Introduction and background}
    \subsection{Motivations}
        \begin{frame}{Nesterov's accelerated gradient in 1983}
            \begin{block}{Nesterov's accelerated gradient in 1983}
                Initialized $x_0 = y_0 \in \RR^n$. 
                The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
                {\small
                \begin{align*}
                    & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
                    \\
                    & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
                    \\
                    & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
                    \\
                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
                \end{align*}    
                }
            \end{block}
            When $F$ is convex and, $L$ Lipschitz smooth. 
            If minimizer $x^+$ exists, then: 
            \begin{itemize}
                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;
                \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
            \end{itemize}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part I}
            Major results from the literature regarding different choices for the momentum sequence $(t_k)_{k \ge 0}$. 
            \begin{block}{Beck, Teboulle 2009 {\cite[Theorem 4.4]{beck_fast_2009-1}}}
                Commonly known by the name FISTA, it allows $(t_k)_{k}$: 
                \begin{align*}
                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
                \end{align*}    
                When $t_k (t_k - 1) = t_{k - 1}^2$, it yields $\mathcal O(1/k^2)$ convergence rate of optimality gap
            \end{block}
            \begin{block}{Chambolle, Dossal 2015 \cite[Theorem 4.1]{chambolle_convergence_2015}}
                If $t_k = (k + a -1)/a$ in which case this gives $\theta_{k} = \frac{k - 2}{k + a - 1}$, then $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.    
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part II}
            A finetuned constant momentum sequence gives optimal linear convergence rate for specific strongly convex objective. 
            \begin{block}{
                Nesterov 2018 {\cite[Theorem 2.2.3]{nesterov_lectures_2018}}, 
                Beck 2017 {\cite[Theorem 10.42]{beck_first-order_2017}}
            }
                If in addition whe $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, and $\mu > 0$ strongly convex, then for $(\theta_k)_{k\ge 0}$ such that: 
                \begin{align*}
                    \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}, 
                \end{align*}
                it gives $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part III}
            The cases when the inequality of Nesterov's rule is not satisfied had been investigated as well.
            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}}
                If $\theta_k = \frac{k}{k + b}\;\forall k \ge 0$ where $b \in (0, 3)$ then, the optimality gap has a convergence rate of $\mathcal O(1/k^{2b/3})$. 
            \end{block}
        \end{frame}

@@

        \begin{frame}{Relaxed Weak Accelerated Proximal Gradient}
            We asked the following major question.  

@@

            We addressed it by what we called: ``Relaxed Weak Accelerated proximal Gradient'' (R-WAPG). 
                \item It's interpreted from the Nesterov's estimating sequence technique and based on the proximal gradient inequality. 
                \item It relaxes the assumption of the momentum sequence parameter while still retaining an upper bound on the optimality gap. 

@@

                    \item A minimizer $x^+$ exists for the optimization problem: $F^+ = \min_x \left\lbrace f(x) + g(x)\right\rbrace$.

@@

            \textbf{This assumption is the full scope of the theoretical and practical discussion.}

@@

            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) has for all $k \ge 1$:

@@

                    F(x_k) - F^+ 
                    \le

@@

            We tried it out on some variants in the literature. 

@@

        \begin{frame}{The numerical experiment that had been inspired}
            Our theories suggest that the upper bound for $F(x_k) - F(x^+)$ in our R-WAPG framework is ultimately described by the sequence $(\alpha_k)_{k \ge 0}$.
            Since $\alpha_k \in (\mu/L, 1)$ and all convex function is strongly convex with strong convexity constant $\mu = 0$, this is what we did:

@@

                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the Bregman Divergence at two successive iterates when the algorithm is running. 
                This information is used to determine the sequence $(\alpha_k)_{k \ge 0}$, and used to visualized our theoretical upper bound. 

@@

            Starting in this section, we will highlight key theoretical results that will allow the unifying convergence rate for Euclidean variants of FISTA in the literature.
            We start off with the following definition. 

@@

            \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}

@@

                Let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ be such that: 
                    \item $\alpha_0 \in (0, 1]$, 
                    \item $\alpha_k \in (\mu/L, 1) \quad (\forall k \ge 1)$, 
                    \item $\rho_k := \frac{\alpha_{k + 1}^2 - (\mu/L) \alpha_{k + 1}}{(1 - \alpha_{k + 1}) \alpha_k^2}$ for all $k \ge 0$. 
                We call the sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 

@@

                The algorithm generates the sequences of vectors $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for all $k\ge 1$ by such that:

@@

@@

                        \left(\gamma_k(1 - \alpha_k) v_k - \alpha_k \mathcal G_L (y_k) + \mu \alpha_k y_k\right),

@@

            After six pages of math in the paper (not necessarily dense), we deduced the following theorem: 

@@

@@

@@

                    x_{k + 1} 
                    &=y_k - L^{-1} \mathcal G_L (y_k),

@@

                    x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k), 
                    y_{k + 1}
                    &= x_{k + 1} +
                    \frac{\rho_{k}\alpha_{k}(1 - \alpha_k)}
                    {\rho_k\alpha_k^2 + \alpha_k}(x_{k + 1} - x_k). 

@@

            When $\mu = 0$, then has:

@@

                If it has $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then:

@@

                    \item Let $t_k := \alpha_k^{-1}$, then it would satisfy $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``inverted FISTA sequence''.

@@

        \begin{frame}{In addition, our theory made one new prediction}

@@

                \item It has $\alpha_k \in (0, 1)$. The sequence $(\alpha_k)_{k \ge 1}$ is as loose as possible. 

@@

            This inspired our numerical experiments. 

@@

\section{References and draft on arxiv}
    \begin{frame}{Acknowledgement}
        The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
        \par
        The travel of HL to this conference is supported by the NSF grant DMS-2526465.
    \end{frame}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}
